\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-19 paper.tex
Subi las primera correciones 18 junio

\subsection{Fabrication of PS  GRIN Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{OJO. No controlaste la temperatura} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
of $1.206\text{cm}^2$. \notaC{Estan son las coordenadas del electrodo} The coordinates the tip of the
electrode at $\bm
r_0=(x_0,y_0,z_0)=(0.1\text{cm},0.3\text{cm},0.9\text{cm})$
\notaL{\sout{¿Cuáles fueron las coordenadas del
  electrodo?}} We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other samples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$.
\subsection{Morphological studies}
\label{sec:morph-stud}
\notaL{Cambié el orden}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
case of a single PS layer we used
the standard formula \cite{T8,T9} \notaL{\sout{referencia}} for three media air (0), PS
(1) and c-Si (2),
 \begin{eqnarray}\label{Eq:ECMR}
   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
\end{eqnarray}
where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
coefficients at the air/PS and PS/c-Si interfaces \cite{T10,T11}\notaL{\sout{referencias}}
and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of thickness $d$.
\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
  la siguiente frase:
The advantage of this method is
the possibility of taking into account the interface roughness effect
by including the Davies-Bennett factor in the coefficient of each
Fresnel cite{I17, I18, I19}, which represents the roughness of a
Gaussian distribution.}} \notaC{No tenia ninguna relevancia en este 
punto de la discusión, y si fue una equivocación dejarla hasta el 
final}

@@

\begin{table}
  \centering
  \begin{tabular}{ccccccc}
    \hline
    Pos(kind)&Current(mA/cm$^2$)&Porosity&Index&Wavelength($\mu\text{m}$)\\
    \hline
    \hline
    A(H) & 5.5 & 0.45& 2.66& 0.65   \\
    A(L) & 44  & 0.74& 1.44& 0.65   \\
    B(H) & 4.0 & 0.41& 2.76& 0.58   \\
    B(L) & 32  & 0.68& 2.29& 0.58   \\
    C(H) & 3.0 & 0.39& 2.81&0.54    \\
    C(L) & 24  & 0.64& 2.30&0.54    \\
  \end{tabular}
  \caption{Some properties of the PS GRIN MC corresponding to the
    positions $A$, $B$ and $C$ and the corresponding high ($H$) and
    low ($L$) index layers. The current densities were obtained by
    scaling the results in Fig. \ref{fig:DR1} with $I_H$ and
    $I_L$, the depths were obtained from the etching
    times and the current density using \eqref{eq:etch}, the porosity
    was obtained from Eq. \eqref{eq:poros}, the indices of refraction
    were obtained from Eq. \eqref{Eq:Brugg} using the porosity, and
    the resonant wavelengths of the cavity were read from
    Fig. \ref{fig:MCGRIN3}.
    \notaL{Inventé lo de arriba. Qué es cierto y qué
      mentira?}\notaL{Por qué resuenas en 0.65 si habías diseñado
      0.67 en A?} \notaL{¿De dónde sacaste
        $\lambda_c$ para los otros puntos? ¿Cómo le hiciste para que
        $\lambda_c$ diera lo mismo en $H$ y en $L$? $n$ y $k$ dependen de la
        frecuencia. ¿Qué frecuencia usaste para darles valores en esta
        tabla?}\notaL{quité digitos a n. quité k pues es chiquita,
        ¿no? quité los tiempos pues son los mismos. Quité las
        posiciones pues están descritas antes. Añade una columna
        con las profundidades $d_H$ y $d_L$. }\notaL{De los rótulos de
      la figura quita las palabras Point. Cambia simulation por Theory.}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} we show a photograph of a PS GRIN MC
sample, which displays a color that shifts towards the blue when we
move towards its right, that is, away from where the electrode was
positioned. In the figure we indicate three points with $x$ coordinates
$x_A=0.3\text{cm}$,  $x_B=0.8\text{cm}$, and $x_C=1.2\text{cm}$
on we measured the reflectance spectra, also shown in the figure.
\notaL{No dices cómo hiciste las curvas teóricas} The spectra have the
expected shape: a high reflectance plateau corresponding to the
photonic band gap of the Bragg mirror, with a deep narrow minimum due
to the Fabry-Perot resonance of the cavity. We also present the
calculated spectra. To that end, we calculated the current density
using the theory developed in Sec. \ref{sec:calc-curr-dens}, i.e., by
scaling Fig. \ref{fig:DR1} with the total current $I_H$ and $I_L$ used
to fabricate each layer. From the current densities we obtained the
corresponding etching rates and the porosities using
Eqs.~\eqref{eq:etch} and  \eqref{eq:poros}, and from the, the
thickness of each layer, the index of refraction
(Eq. \eqref{Eq:Brugg}) and the reflectance,using standard transfer
matrix theory \notaL{ref}. Notice the good agreement between theory
and experiment. \notaL{No me lo creo. Me sospecho que más bien,
  ajustaste el experimento no sé con qué parámetro. Explícame cómo
  hiciste el cálculo.} The parameters used are shown in Table \ref{tabla:1}.
\notaL{No entiendo qué quisiste decir aquí: For theoretical values, we
  use complex refractive indices as free parameters to fit the
  experimental refractive spectra (Section 4.2).} The band-gap, the
resonance and the oscillations due to multiple reflections in the
region of transparency are similar, though the experimental spectra is
more rounded and the central resonance is wider. This might be due to
the roughness of the interfaces, which would lead to some scattering
whose effects are similar to those of an additional absorption
\ref{cita el artículo en prensa de Guille y mío}.\notaL{Checar que no
  diga mentiras arriba. El ajuste es demasiado bueno, pero no sé cómo
  se hizo. Hay que explicar qué significan y de dónde salieron las
  $\lambda_c$ de la tabla. }

>>>>

\subsection{Fabrication of PS  GRIN Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{OJO. No controlaste la temperatura} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
of $1.206\text{cm}^2$. \notaC{Estan son las coordenadas del electrodo} 
The coordinates the tip of the electrode at $\bm
r_0=(x_0,y_0,z_0)=(0.1\text{cm},0.3\text{cm},0.9\text{cm})$
\notaL{\sout{¿Cuáles fueron las coordenadas del
  electrodo?}} We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$, which required an attack time of
$t_1=600 \text{s}$ and other samples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$ and $t_2=200 \text{s}$ . \notaC{
Coloque los tiempo de ataque para $t_1$ y $t_2$}
\subsection{Morphological studies}
\label{sec:morph-stud}
\notaL{Cambié el orden}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
case of a single PS layer we used
the standard formula \cite{T8,T9} \notaL{\sout{referencia}} for three media air (0), PS
(1) and c-Si (2),
 \begin{eqnarray}\label{Eq:ECMR}
   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
\end{eqnarray}
%where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
coefficients at the air/PS and PS/c-Si interfaces \cite{T10,T11}
and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of thickness $d$.
\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
  la siguiente frase:
The advantage of this method is
the possibility of taking into account the interface roughness effect
by including the Davies-Bennett factor in the coefficient of each
Fresnel cite{I17, I18, I19}, which represents the roughness of a
Gaussian distribution.} \notaC{No tenia ninguna relevancia en este 
punto de la discusión, y si fue una equivocación dejarla hasta el final}

@@

\begin{table}
  \centering
  \begin{tabular}{ccccccc}
    \hline
    Pos(kind)&Current(mA/cm$^2$)&Porosity&Index&Wavelength($\mu\text{m}$)\\
    \hline
    \hline
    A(H) & 5.5 & 0.45& 2.66& 0.65   \\
    A(L) & 44  & 0.74& 1.44& 0.65   \\
    B(H) & 4.0 & 0.41& 2.76& 0.58   \\
    B(L) & 32  & 0.68& 2.29& 0.58   \\
    C(H) & 3.0 & 0.39& 2.81&0.54    \\
    C(L) & 24  & 0.64& 2.30&0.54    \\
  \end{tabular}
  \caption{Some properties of the PS GRIN MC corresponding to the
    positions $A$, $B$ and $C$ and the corresponding high ($H$) and
    low ($L$) index layers. The current densities were obtained by
    scaling the results in Fig. \ref{fig:DR1} with $I_H$ and
    $I_L$, the depths were obtained from the etching
    times and the current density using \eqref{eq:etch}, the porosity
    was obtained from Eq. \eqref{eq:poros}, the indices of refraction
    were obtained from Eq. \eqref{Eq:Brugg} using the porosity, and
    the resonant wavelengths of the cavity were read from
    Fig. \ref{fig:MCGRIN3}.
    \notaL{Inventé lo de arriba. Qué es cierto y qué
      mentira?}\notaL{Por qué resuenas en 0.65 si habías diseñado
      0.67 en A?} \notaL{¿De dónde sacaste
        $\lambda_c$ para los otros puntos? ¿Cómo le hiciste para que
        $\lambda_c$ diera lo mismo en $H$ y en $L$? $n$ y $k$ dependen de la
        frecuencia. ¿Qué frecuencia usaste para darles valores en esta
        tabla?}\notaL{quité digitos a n. quité k pues es chiquita,
        ¿no? quité los tiempos pues son los mismos. Quité las
        posiciones pues están descritas antes. Añade una columna
        con las profundidades $d_H$ y $d_L$. }\notaL{De los rótulos de
      la figura quita las palabras Point. Cambia simulation por Theory.}}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} we show a photograph of a PS GRIN MC
sample, which displays a color that shifts towards the blue when we
move towards its right, that is, away from where the electrode was
positioned. In the figure we indicate three points with $x$ coordinates
$x_A=0.3\text{cm}$,  $x_B=0.8\text{cm}$, and $x_C=1.2\text{cm}$
on we measured the reflectance spectra, also shown in the figure.
\notaL{No dices cómo hiciste las curvas teóricas} The spectra have the
expected shape: a high reflectance plateau corresponding to the
photonic band gap of the Bragg mirror, with a deep narrow minimum due
to the Fabry-Perot resonance of the cavity. We also present the
calculated spectra. To that end, we calculated the current density
using the theory developed in Sec. \ref{sec:calc-curr-dens}, i.e., by
scaling Fig. \ref{fig:DR1} with the total current $I_H$ and $I_L$ used
to fabricate each layer. From the current densities we obtained the
corresponding etching rates and the porosities using
Eqs.~\eqref{eq:etch} and  \eqref{eq:poros}, and from the, the
thickness of each layer, the index of refraction
(Eq. \eqref{Eq:Brugg}) and the reflectance,using standard transfer
matrix theory \notaL{ref}. Notice the good agreement between theory
and experiment. \notaL{No me lo creo. Me sospecho que más bien,
  ajustaste el experimento no sé con qué parámetro. Explícame cómo
  hiciste el cálculo.} The parameters used are shown in Table \ref{tabla:1}.
\notaL{No entiendo qué quisiste decir aquí: For theoretical values, we
  use complex refractive indices as free parameters to fit the
  experimental refractive spectra (Section 4.2).} The band-gap, the
resonance and the oscillations due to multiple reflections in the
region of transparency are similar, though the experimental spectra is
more rounded and the central resonance is wider. This might be due to
the roughness of the interfaces, which would lead to some scattering
whose effects are similar to those of an additional absorption
ref{cita el artículo en prensa de Guille y mío}.\notaL{Checar que no
  diga mentiras arriba. El ajuste es demasiado bueno, pero no sé cómo
  se hizo. Hay que explicar qué significan y de dónde salieron las
  $\lambda_c$ de la tabla. }
